Plots for Latent Hawkes Paper

### 2020-07-15 output_scripts/Paper_Plots.Rmd
finish plots for paper

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

The aim of this notebook is a way to quickly and efficiently create all the plots
required for this paper. They will be built with the current fits and models.

@@

# Figure 4:
To be added.

# Figure 5:
To be added.

>>>>

library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

<!-- The aim of this notebook is a way to quickly and efficiently create all the plots -->
<!-- required for this paper. They will be built with the current fits and models. -->

@@

# Figure 4:

## Figure 4a Recover Latent Ranks
```{r fig-4a}
sim_data_path <- "../output/sims_long/"

load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
load(paste(sim_data_path,"fit123_state_est.RData",sep=''))

n_sim <- 50

#png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
par(mfrow=c(3, length(object_par$f_vec_1)),
    mar=c(0,0,1,0),
    oma=c(6.5,11,3.5,1))

y.ub <- c(12,12,12,12,12)
text.y <- c(rep(8,4),8)
text.x <- c(0.1,0.2,0.4,0.7,0.9)
text.x.adj <- c(0.3,0.4,0.6,0.5,0.8)
model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)

for(m in c(1:3)){
  for(j in c(1:length(object_par$f_vec_1))){
    plot(1,4,xlim=c(0,1),ylim=c(0,y.ub[j]),
         type="n",xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[1001:2000,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

    ## plot true value
    abline(v=object_par$f_vec_1[j],lwd=1.8,lty=2,col="gray30")

    ## plot box
    box.wdt <- 1.5
    box.col <- "black"
    box(lty = 'solid',col=box.col,lwd=0.7)

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2.4)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
        at=0.5)
  ## top
  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=3,
        at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=2, las=2)
}

## Figure 4b: Recover Latent States

```{r prepare data for 4b}
plot.s <- 9
plot.i <- 4
plot.j <- 5

cur_i <- 4
cur_j <- 5

test.mmhp <- sim_model3_data[plot.s][[1]]$mmhp_matrix[plot.i,plot.j][[1]]
temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0,tail(temp.t,1),length.out=5000)

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0=model1_par_est$lambda0,
                                                 alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                                           model1_par_est$f[plot.j],
                                                                           model1_par_est$eta_1,
                                                                           model1_par_est$eta_2,
                                                                           model1_par_est$eta_3),
                                                 beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],2,mean),
                       zeta=apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))

lambda.m2<-uniHawkesIntensityNumeric(object=list(lambda0=model2_par_est$gamma[plot.i]+
                                                   model2_par_est$zeta[plot.j],
                                                 alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                                           model2_par_est$f[plot.j],
                                                                           model2_par_est$eta_1,
                                                                           model2_par_est$eta_2,
                                                                           model2_par_est$eta_3),
                                                 beta=model2_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## Model3
#############
mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[plot.s]]$lambda0[1001:2000]),
                     lambda1=mean(sim_model3_stan_sim3[[plot.s]]$lambda1[1001:2000]),
                     eta_1=mean(sim_model3_stan_sim3[[plot.s]]$eta_1[1001:2000]),
                     eta_2=mean(sim_model3_stan_sim3[[plot.s]]$eta_2[1001:2000]),
                     eta_3=mean(sim_model3_stan_sim3[[plot.s]]$eta_3[1001:2000]),
                     beta=mean(sim_model3_stan_sim3[[plot.s]]$beta[1001:2000]),
                     f=apply(sim_model3_stan_sim3[[plot.s]]$f[1001:2000,],2,mean))

object_hat <- list(lambda0=mmhp_par_est$lambda0,
                   lambda1=mmhp_par_est$lambda1,
                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta=mmhp_par_est$beta,
                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

## don't have these parameters....?
state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp, termination=200)

# where is fixInterpolateState?...
# this is in one of the files at the top of latent_simulation.Rmd
# drawIntensity.R

step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)

lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
                                  t=temp.t[-1],
                                  time.vec=time.segment,
                                  latent.vec=step.fun.est(time.segment))

object_true <- lapply(object_matrix,function(x) x[plot.i,plot.j])
names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")

lambda.true <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
                                        latent=list(x=fixStateTransition(test.mmhp)$x,
                                                    z=fixStateTransition(test.mmhp)$z),
                                        time.vec=time.segment)

```{r fig4b-recover-latent-states}
y.ub <- c(130,72,31)
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#130
my.long.x <- 205#134.5
legend.x <- c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
# negative.col <- add.alpha('lightskyblue',0.6)
# positive.col <- add.alpha('tomato',0.6)
negative.col <- viridis::viridis(5,alpha = 0.6)[1]
positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

# model1
############
true.object <- object_true

drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[1], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim,
                          title_name=paste(plot.i,"->",plot.j),
                          title.cex = 2,
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model1_par_est$lambda0,

                         alpha=model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                                   model1_par_est$f[plot.j],
                                                   model1_par_est$eta_1,
                                                   model1_par_est$eta_2,
                                                   model1_par_est$eta_3),
                         beta=model1_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[1],
                                         alpha=line.alpha[2]),
                         line.width=line.wdth[2])

## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
# axis(2,at=c(-10,y.ub[1]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-10,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

## add legend
# changed 34 to 23, 25 to 18, -20 to -10
legend(20,104,c("State 1/0 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(29,84,pch=1,cex=2,col="blue")
points(26,84,pch=16,cex=2,col="blue")
legend(legend.x[1],legend.y[1],c("True"),
       col = c("black"),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)
legend(legend.x[1]+18,legend.y[1],c("C-HP"),
       col = c(model_colors[1]),
       y.intersp=0.88,x.intersp=0.15,bty = "n",
       lty = c(1), lwd = c(5), cex=legend.cex,seg.len=1)

# legend(93,24,c("Overestimation","Underestimation"),
#        col = c(positive.col,negative.col),
#        y.intersp=0.88,x.intersp=0.5,bty = "n",
#        lty = c(1,1), lwd = c(20,20), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-4,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,200),
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200),
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
# change -0.7 to -0.5 and -0.5 to -0.25
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(2,at=c(-2,y.ub[1]),col="gray35",
#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-2,y.ub[1]),col="gray35",
#      line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

# model2
############
drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[2], 
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawHawkesIntensityPaper(lambda0=model2_par_est$gamma[plot.i]+
                           model2_par_est$zeta[plot.j],
                         alpha=model1_fn$alpha.fun(model2_par_est$f[plot.i],
                                                   model2_par_est$f[plot.j],
                                                   model2_par_est$eta_1,
                                                   model2_par_est$eta_2,
                                                   model2_par_est$eta_3),
                         beta=model2_par_est$beta,
                         events=test.mmhp$tau,
                         color=add.alpha(model_colors[2], alpha=line.alpha[2]),line.width=line.wdth[2])
legend(legend.x[2],legend.y[2],"C-DCHP",
       col = model_colors[2],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty = 1, lwd = 5, cex= legend.cex,seg.len=1)
## draw box
# -20 to -10 to -5 here
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
# axis(2,at=c(-5,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-5,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

## delta lambda
par(mar = c(0,0.3,0,0.1))
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), ylim=c(-3,10), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
#### hiding these for now ####
polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(2,at=c(-20,y.ub[2]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-20,y.ub[2]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

# model3
########
par(mar = c(0,0.3,1,0.1))
drawUniMMHPIntensityPaper(true.object,simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[3], color=add.alpha("black", alpha=line.alpha[1]),line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawUniMMHPIntensityPaper(object_hat,simulation=list(
  x=state.est.latent.mmhp.new$x.hat,                                               
  z=state.est.latent.mmhp.new$z.hat,
  tau=test.mmhp$tau,zt=test.mmhp$zt,
  lambda.max=test.mmhp$lambda.max),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                      alpha=line.alpha[2]),
  line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)
# axis(2,at=c(-20,y.ub[3]),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(3,at=c(-5,my.long.x),col="gray35",line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-20,y.ub[3]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

legend(55,32,c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.88,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-12,8), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,200), c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,200), c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(2,at=c(-20,y.ub[1]),col="gray35",
#      line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)
# axis(4,at=c(-20,y.ub[1]),col="gray35",line=-0.5,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
```

# Figure 5:
```{r data for fig 5}
load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
## Initialize
N_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
Lambda_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
KS_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))

## Iteration on 50 simulations
for(s in c(1:n_sim)){
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
                                        cut_off = cut_off, N = length(object_par$f_vec_1))

  N_array[s,,] <- clean_sim_data$N_count

  ## model 1
  #########
  model1_par_est <- list(lambda0=mean(sim_model3_stan_sim1[[s]]$lambda0[1001:2000]),
                         eta_1=mean(sim_model3_stan_sim1[[s]]$eta_1[1001:2000]),
                         eta_2=mean(sim_model3_stan_sim1[[s]]$eta_2[1001:2000]),
                         eta_3=mean(sim_model3_stan_sim1[[s]]$eta_3[1001:2000]),
                         beta=mean(sim_model3_stan_sim1[[s]]$beta[1001:2000]),
                         f=apply(sim_model3_stan_sim1[[s]]$f[1001:2000,],2,mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
      m1_object <- list(lambda0=model1_par_est$lambda0,
                        alpha=model1_fn$alpha.fun(model1_par_est$f[i],model1_par_est$f[j],model1_par_est$eta_1,model1_par_est$eta_2,model1_par_est$eta_3),
                        beta=model1_par_est$beta)
      Lambda_model1_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
                                                             events=current_t,
                                                             termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object=m1_object, events=current_t)
      KS_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model1_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model1_array[s,i,j] <- uniHawkesPearsonResidual(object=m1_object, 
                                                         events=current_t,
                                                         termination = tail(current_t,1))
    }
  }

  ## model2
  #############
  model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[s]]$gamma[1001:2000,],2,mean),
                         zeta=apply(sim_model3_stan_sim2[[s]]$zeta[1001:2000,],2,mean),
                         eta_1=mean(sim_model3_stan_sim2[[s]]$eta_1[1001:2000]),
                         eta_2=mean(sim_model3_stan_sim2[[s]]$eta_2[1001:2000]),
                         eta_3=mean(sim_model3_stan_sim2[[s]]$eta_3[1001:2000]),
                         beta=mean(sim_model3_stan_sim2[[s]]$beta[1001:2000]),
                         f=apply(sim_model3_stan_sim2[[s]]$f[1001:2000,],2,mean))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      current_t <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]$tau
      m2_object <- list(lambda0=model2_par_est$gamma[i]+model2_par_est$zeta[j],
                        alpha=model1_fn$alpha.fun(model2_par_est$f[i],model2_par_est$f[j],model2_par_est$eta_1,model2_par_est$eta_2,model2_par_est$eta_3),
                        beta=model2_par_est$beta)
      Lambda_model2_array[s,i,j]<-uniHawkesIntegralIntensity(object=m1_object, 
                                                             events=current_t,
                                                             termination = tail(current_t,1))
      Lambda_test <- uniHawkesCompensator(object=m2_object, events=current_t)
      KS_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$statistic
      KS_p_model2_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      PR_model2_array[s,i,j] <- uniHawkesPearsonResidual(object=m2_object, 
                                                         events=current_t,
                                                         termination = tail(current_t,1))
    }
  }

  ## Model3 & true model
  ######
  mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[s]]$lambda0[1001:2000]),
                       lambda1=mean(sim_model3_stan_sim3[[s]]$lambda1[1001:2000]),
                       eta_1=mean(sim_model3_stan_sim3[[s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim3[[s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim3[[s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim3[[s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim3[[s]]$f[1001:2000,],2,mean))
  clean_sim_data <- cleanSimulationData(raw_data=sim_model3_data[s][[1]], 
                                        cut_off = cut_off, N = length(object_par$f_vec_1))

  for(i in c(1:5)){
    for(j in c(1:5)[-i]){
      test.mmhp <- sim_model3_data[s][[1]]$mmhp_matrix[i,j][[1]]
      temp.t <- test.mmhp$tau
      current.n <- length(temp.t)-1
      time.segment <- seq(0,tail(temp.t,1),length.out=10000)

      object_hat <- list(lambda0=mmhp_par_est$lambda0,
                         lambda1=mmhp_par_est$lambda1,
                         alpha=model3_fn$alpha.fun(mmhp_par_est$f[i],
                                                   mmhp_par_est$f[j],
                                                   mmhp_par_est$eta_1,
                                                   mmhp_par_est$eta_2),
                         beta=mmhp_par_est$beta,
                         q1=model3_fn$q1.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3),
                         q2=model3_fn$q0.fun(mmhp_par_est$f[i],
                                             mmhp_par_est$f[j],
                                             mmhp_par_est$eta_3))

      object_true <- lapply(object_matrix,function(x) x[i,j])
      names(object_true) <- c("lambda0","lambda1","alpha","beta","q1","q2")

      ## est Lmabda and [R]
      Lambda.test <- mmhpCompensator(params=object_hat, 
                                     t=temp.t,
                                     pzt=2-event_state_est_lst[[s]][i,j][[1]]$zt_v,
                                     if.pzt=FALSE)
      KS_model3_array[s,i,j] <-  ks.test(Lambda.test,"pexp")$statistic
      KS_p_model3_array[s,i,j] <-  ks.test(Lambda_test,"pexp")$p.value
      state.est.latent.mmhp <- interpolate_state_est_lst[[s]][i,j][[1]]
      step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,2-state.est.latent.mmhp$z.hat)
      est.intensity <- mmhpIntensityNumeric(params=object_hat,
                                            t=temp.t[-1],
                                            time.vec=time.segment,
                                            latent.vec=step.fun.est(time.segment))
      est.intensity.events <- mmhpIntensityAtEvents(params=object_hat, t=temp.t,
                                                    latent_z=event_state_est_lst[[s]][i,j][[1]]$zt_v)
      Lambda_model3_array[s,i,j] <- sum(est.intensity)*(time.segment[2]-time.segment[1])
      PR_model3_array[s,i,j] <- sum(1/sqrt(est.intensity.events))-
        sum(sqrt(est.intensity))*(time.segment[2]-time.segment[1])

      ## Under the true model
      Lambda.test.true <- mmhpCompensator(params=object_true,
                                          t=temp.t,
                                          pzt=2-test.mmhp$zt[2:length(test.mmhp$zt)],
                                          if.pzt=FALSE)
      KS_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$statistic
      KS_p_true_array[s,i,j] <-  ks.test(Lambda.test.true,"pexp")$p.value
      true.intensity <- mmhpTrueIntensityNumeric(params=object_true, t=temp.t,
                                                 latent=list(x=fixStateTransition(test.mmhp)$x,
                                                             z=fixStateTransition(test.mmhp)$z),
                                                 time.vec=time.segment)
      true.intensity.events <- mmhpIntensityAtEvents(params=object_true, t=temp.t, 
                                                     latent_z=test.mmhp$zt)
      Lambda_true_array[s,i,j] <- sum(true.intensity$lambda.t)*(time.segment[2]-time.segment[1])
      PR_true_array[s,i,j] <- sum(1/sqrt(true.intensity.events))-
        sum(sqrt(true.intensity$lambda.t))*(time.segment[2]-time.segment[1])
    }
  }
}
